\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-04-17 paper.tex
monad section was updated

There exists a certain complexity when it comes to grasping to concept of a monad. From history, monads were initially adopted in Haskell to produce input and output operations. However, the capabilities of monads were not bound to just I/O. Additionally, monads can support multiple operations such as state, non-determinism, continuations, exceptions etc. \\ \\ 
The default monad is defined by three components: 
\begin{itemize}
    \item a type constructor
    \item a function return
    \item a bind operator ($\gg$=)
\end{itemize}

>>>>

There exists a certain complexity when it comes to grasping to concept of a monad. From history, monads were initially adopted in Haskell to produce input and output operations. However, the capabilities of monads were not bound to just I/O. Additionally, monads can support multiple operations such as state, non-determinism, continuations, exceptions etc. \\ \\ 
The default monad is composed by three esential components: 
\begin{itemize}
    \item a type constructor
    \item a function return
    \item a bind operator ($\gg$=)
\end{itemize}
The \textit{return} function and the bind operator ($\gg$=) have the following types:

\begin{center}
   return   :: a $\rightarrow$ m a \\
   ($\gg$=) :: m a $\rightarrow$ (a $\rightarrow$ m b) $\rightarrow$ m b 
   \end{center}
In order for the above function definitions to hold, the three monadic laws need to be satisfied.

The Maybe monad has been selected to provide a concrete insight on how a monad functions.
